Multiple Dice Working as One: CAD Flows and Routing Architectures for Silicon Interposer FPGAs

### 2015-07-01 doc/journal/fpgapaperfinal/FPGAPaper/partitioning.tex
Shortened a few equation variables and fixed a few confusing sentences.
git-svn-id: https://vtr-verilog-to-routing.googlecode.com/svn/branches/javeed@4610 8e3573b8-cf2c-4f14-ef6d-137439e28b8b
Ehsan: Making updates based on reviewer's comments. Done with almost all of edits that were assigned to me (see response_to_reviewers.txt). (i just have to summarize a section in case we run out of space). I also need to get runtime measurements to present to one of the reviewers, but that's not going to be added to the paper.
git-svn-id: https://vtr-verilog-to-routing.googlecode.com/svn/branches/javeed@4

The current version of hMetis does not support heterogeneous balance constraints, though Metis does. Metis was used in our CAD flow. However, as the circuit netlist is naturally represented as a hypergraph, it needs to be transformed to a graph before Metis can process it.

@@

\subsection{\% wires cut}
To evaluate the CAD flow performance for a range of interposer architectures, we varied the fraction of wires cut and measured the average minimum channel width over the 8 largest VTR circuits. As shown in Figure \ref{fig:wires_cut}, this new flow is a significant improvement over that of~\cite{interposer2014} for FPGAs where more than half the wires are cut at interposer boundaries. It is slightly worse than the traditional FPGA CAD flow even for an architecture with 0\% of the wires cut, which is a monolithic FPGA, presumably because we have restricted the placer's freedom.

>>>>

The current version of hMetis does not support heterogeneous balance constraints, though Metis does, so we use Metis in our CAD flow. However, as the circuit netlist is naturally represented as a hypergraph, it needs to be transformed to a graph before Metis can process it.

@@

\subsection{\% wires cut}
To evaluate the CAD flow performance for a range of interposer architectures, we varied the fraction of wires cut and measured the average minimum channel width over the 8 largest VTR circuits. As shown in Figure \ref{fig:wires_cut}, this new flow is a significant improvement over that of~\cite{interposer2014} for FPGAs where more than half the wires are cut at interposer boundaries. \hl{But it is slightly worse than the traditional FPGA CAD flow for an architecture with 0\% of the wires cut}, which is a monolithic FPGA, presumably because we have restricted the placer's freedom.
